Contribution Title\thanks{Supported by organization x.}

### 2019-11-07 sections/evaluation.tex
added marco's for comments.
make change to optimization 1

\subsection{Reduce Clause Size with $\IUIP$}
To evaluate the effectiveness of $\IUIP$ as a clause reduction technique, we implement  $\IUIPPURE$ and $\IUIPMIN$  on top of \text{\MapleBase} \cite{}, the winner of SAT Race 2015 application track.  We than compare the performance of the baseline $\MapleBase$ with $\MapleIUIPPURE$ and $\MapleIUIMIN$ on the full set of benchmarks from SAT RACE 2019 main track.

@@

Inserted a table here, and graphs and analysis

\begin{center}
\begin{tabular}{ | m{4cm} | m{2cm}| m{2cm} | m{2cm} | m{2cm} | } 
\hline
Solver & \# solved & PAR-2 & Clause Size & Memory \\ 
\hline
$\MapleBase$ & cell5 & cell6 & cell 7 & cell 8 \\ 
\hline
$\MapleIUIPPURE$ & cell8 & cell9 & cell10 & cell11\\ 
\hline
$\MapleIUIMIN$ & cell8 & cell9 & cell10 & cell11\\ 
\hline
\end{tabular}
\end{center}

A solver produce smaller clauses can construct smaller proofs as well. For UNSAT instances, we additionally measure their DRUP\cite{} proof checking time as well as the size of the optimized DRUP proof. We used DART-trim \cite{} with 10000 timeout to check and optimize DRUP proofs.

Insert a comparison graphs here.

>>>>

\subsection{Clause Reduction with $\IUIP$}
To evaluate $\IUIP$'s effectiveness as a clause reduction technique, we implement  $\IUIPPURE$ and $\IUIPMIN$  on top of \text{\MapleBase} \cite{}, the winner of SAT Race 2015 application track.  We than compare the performance of the baseline $\MapleBase$ with $\MapleIUIPPURE$ and $\MapleIUIMIN$ on the full set of benchmarks from SAT RACE 2019 main track.

@@

\nf{Inserted a table here, and graphs and analysis}

\begin{center}
\begin{tabular}{ | m{3.5cm} | m{2cm}| m{2cm} | m{2cm} | m{2cm} | } 
\hline
Solver & \# solved & PAR-2 & Clause Size & Memory \\ 
\hline
$\MapleBase$ & cell5 & cell6 & cell 7 & cell 8 \\ 
\hline
$\MapleIUIPPURE$ & cell8 & cell9 & cell10 & cell11\\ 
\hline
$\MapleIUIMIN$ & cell8 & cell9 & cell10 & cell11\\ 
\hline
\end{tabular}
\end{center}

A solver produce smaller clauses can construct smaller proofs as well. For UNSAT instances, we additionally measure their DRUP\cite{} proof checking time as well as the size of the optimized DRUP proof. We used DART-trim \cite{} with 5000 timeout to check and optimize DRUP proofs.

\nf{Insert a comparison graphs here. (X and Y comparisons graph, showing both time and optimized proof size).}

\subsection{$\IUIP$ as a Practical Learning Scheme}
To evaluate $\IUIP$'s effectiveness as a clause learning scheme, we implement $\IUIPMIN$ on $\MapleBase$ with $\IUIPGreedy$ (sec~\ref{sec:greedy}) and two variable activity adjustment heuristics,  $\IUIPActive$ and $\IUIPDist$ (sec~\ref{sec: varajust}).

### 2019-11-07 sections/i_uip.tex
make change to optimization 1

\begin{algorithm}[t]
\caption{Control-$\IUIP$}\label{alg:enableCondition}
\begin{algorithmic}[1]
\Require  $\oneUIPClause$ is a valid 1-UIP clause
\Require  $ t_{gap} \ge 0$ is a dynamically calculated gap threshold
\Procedure{Control-$\IUIP$}{$\oneUIPClause,  t_{gap}$} 
    \State $Gap \gets |\oneUIPClause| - \textit{LBD}(\oneUIPClause)$
     \If{$Gap > t_{gap}$} \label{ln:compareGap}
        \State $\iUIPClause \gets \IUIP(\oneUIPClause, \phi)$
        \If {$|\iUIPClause| < |\oneUIPClause|$} 
            \State $\text{Succeed} \gets \text{Succeed}+1$ \label{ln:updateS}
        \EndIf
        \State $\text{Attempted} \gets \text{Attempted}+1$ \label{ln:updateA}
     \EndIf
\EndProcedure
\end{algorithmic}
\end{algorithm}

@@

\subsection{Greedy Active Clause Selection}
Even though $\IUIP$ learning can reduce the size of the learnt clause $\iUIPClause$, but it may introduce inactive literals into $\iUIPClause$.  Inactive literals prevents the clause from being asserted to force literal implication. Therefore, a practical clause learning scheme should consider both size and variable activity. We propose an optional extension $\IUIPGreedy$ to filter out inactive $\oneUIPClause$.

\begin{algorithm}[t]
\caption{$\IUIPGreedy$}\label{alg:greedySelection}
\begin{algorithmic}[1]
\Require  $\oneUIPClause$ is a valid 1-UIP clause
\Require  $\assertionTrail$ is a valid assertion trail
\Procedure{$\IUIPGreedy$}{$\oneUIPClause,  \assertionTrail$} 
   \State $\iUIPClause \gets \IUIP(\oneUIPClause, \assertionTrail)$
   \If{$|\iUIPClause| < |\oneUIPClause| \wedge (\code{AvgVarAct}(\iUIPClause) > \code{AvgVarAct}(\oneUIPClause)) $} \label{ln:checkSizeAndActivity}
    \State \textbf{return} $\iUIPClause$
\Else
    \State \textbf{return} $\oneUIPClause$
\EndIf  \label{ln:cSizeCheck}
\EndProcedure
\end{algorithmic}
\end{algorithm}

@@

\subsection{Adjust Variable Activity}
Two popular branching heuristics for modern SAT solvers are VSIDS and LBR. Both heuristics increase 
the variable activity for all literals involved in resolutions during 1-UIP learning. Since $\IUIP$ extends 1-UIP with deeper resolutions against the trail, the variables activities for the fresh literals involved in the additional resolution steps need to be adjusted as well. We purpose two optional schemes for adjusting variable activities, $\IUIPActive$ and $\IUIPDist$.

>>>>

\begin{algorithm}[t]
\caption{Control-$\IUIP$}\label{alg:enableCondition}
\begin{algorithmic}[1]
\Require  $\oneUIPClause$ is a valid 1-UIP clause
\Require  $ t_{gap} \ge 0$ is a dynamically calculated gap threshold
\Procedure{Control-$\IUIP$}{$\oneUIPClause,  t_{gap}$} 
    \State $Gap \gets |\oneUIPClause| - \textit{LBD}(\oneUIPClause)$
     \If{$Gap > t_{gap}$} \label{ln:compareGap}
        \State $\iUIPClause \gets \IUIP(\oneUIPClause, \phi)$
        \State \textcolor{gray}{\textbf{I-UIP-Greedy}($\iUIPClause$ , $\oneUIPClause$)}  \Comment{additional clause selection policy, see sec~\ref{sec:greedy}}
        \If {$|\iUIPClause| < |\oneUIPClause|$} 
            \State $\text{Succeed} \gets \text{Succeed}+1$ \label{ln:updateS}
        \EndIf
        \State $\text{Attempted} \gets \text{Attempted}+1$ \label{ln:updateA}
     \EndIf
\EndProcedure
\end{algorithmic}
\end{algorithm}

@@

\subsection{Greedy Active Clause Selection} \label{sec:greedy}
Even though $\IUIP$ learning can reduce the size of the learnt clause $\iUIPClause$, but it may introduce literals with low variable activity into $\iUIPClause$.  Inactive literals prevents the clause from being asserted to force literal implication. Therefore, a practical clause learning scheme should consider both size and variable activity. We propose an optional extension $\IUIPGreedy$ to filter out inactive $\oneUIPClause$.

\begin{algorithm}[t]
\caption{$\IUIPGreedy$}\label{alg:greedySelection}
\begin{algorithmic}[1]
\Require  $\iUIPClause$ is a valid i-UIP clause
\Require  $\oneUIPClause$ is a valid 1-UIP clause
\Procedure{$\IUIPGreedy$}{$\iUIPClause, \oneUIPClause$} 
   \If{$|\iUIPClause| < |\oneUIPClause| \wedge (\code{AvgVarAct}(\iUIPClause) > \code{AvgVarAct}(\oneUIPClause)) $} \label{ln:checkSizeAndActivity}
    \State \textbf{return} $\iUIPClause$
\Else
    \State \textbf{return} $\oneUIPClause$
\EndIf  \label{ln:cSizeCheck}
\EndProcedure
\end{algorithmic}
\end{algorithm}

@@

\subsection{Adjust Variable Activity} \label{sec: varajust}
Two popular branching heuristics for modern SAT solvers are VSIDS and LBR. Both heuristics increase 
the variable activity for all literals involved in resolutions during 1-UIP learning. Since $\IUIP$ extends 1-UIP with deeper resolutions against the trail, the variables activities for the fresh literals involved in the additional resolution steps need to be adjusted as well. We purpose two optional schemes for adjusting variable activities, $\IUIPActive$ and $\IUIPDist$.
